Figure Extra

### 2022-09-08 Figures/Figures_nonTCGA.Rmd
Spliting corrplot fuction

```{r}
library(tidyverse)
library(Hmisc)
library(ggridges)
library(ggtext)
library(glue)
```

@@

################################################################################
benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(get(key), levels = get(key)))

@@

  return(ct_corrplots)
}

@@

dict_GSE72056[["CD226"]] <- list(B = c("B"),
                                     CAFs = c(),
                                     CD4 = c("CD4"),
                                     CD8 = c("CD8"),
                                     Endothelial = c(),
                                     Macrophages = c("M1", "M2"),
                                     NK = c("NK"),
                                     Th = c(),
                                     Treg = c(),
                                     Cancer = c(),
                                     Other = c("Mono", "Neu"))

@@

```{r}
benchmark_corrplots(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples", title = "GSE72056")
# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
# 
# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```

@@

```{r}
benchmark_corrplots(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_Thomas,  key = "Samples", title = "Thomas")
# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
# 
# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```

>>>>

```{r}
library(tidyverse)
library(Hmisc)
library(ggridges)
library(ggtext)
library(reshape2)
library(glue)
```

@@

################################################################################
```

```{r}
benchmark_corrplots <- function(deconv_data, true_estimates, dict, key, title){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(get(key), levels = get(key)))

@@

  return(ct_corrplots)
}
```

```{r}
```

@@

# dict_GSE72056[["CD226"]] <- list(B = c("B"),
#                                      CAFs = c(),
#                                      CD4 = c("CD4"),
#                                      CD8 = c("CD8"),
#                                      Endothelial = c(),
#                                      Macrophages = c("M1", "M2"),
#                                      NK = c("NK"),
#                                      Th = c(),
#                                      Treg = c(),
#                                      Cancer = c(),
#                                      Other = c("Mono", "Neu"))

@@

```
## Corrplot
```{r}
corr <- benchmark_corr(deconv_data = deconv_GSE72056, true_estimates = truth_GSE72056, dict = dict_GSE72056, key = "Samples")
p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "GSE72056")
p

## Test without function
```{r}

deconv_data = deconv_GSE72056
true_estimates = truth_GSE72056
dict = dict_GSE72056
key = "Samples"
title = "GSE72056"

# build the data
true_subset_ <- true_estimates %>%  na.exclude() %>%
  arrange(factor(get(key), levels = get(key)))

  corr_df <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2))
  write.csv( corr_df, paste0('Spearmans_Correlation_',title,'.csv') )
  corr_df %>% ggplot(aes(measure1, measure2, fill=r, label=round(r_if_sig,2))) +
              geom_tile() +
              labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, subtitle="Only significant correlation coefficients shown (95% I.C.)") +
              scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
              geom_text() + theme_classic() + rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown()) +
              scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
              scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) 
  # order columns by number of NA (push empty columns to the right)
corr_matrix <- corr_df %>%
    dcast(measure2~measure1, value.var = "r") 
corr_matrix_sorted <- corr_matrix[order(rowSums(is.na(corr_matrix))), ]
corr_matrix_sorted2 <- corr_matrix_sorted[,order(colSums(is.na(corr_matrix_sorted))) ]

melt(data = corr_matrix_sorted2) %>% ggplot(aes(measure2, variable, fill=value, label=round(value,2))) +
            geom_tile() + 
            labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= title, subtitle="Only significant correlation coefficients shown (95% I.C.)") +
            scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1), na.value = 'white') +
            geom_text() + theme_classic() + rotate_x_text(angle = 45) + theme(axis.text.x=element_markdown()) + theme(axis.text.y=element_markdown()) +
            scale_x_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red")) +
            scale_y_discrete(expand=c(0,0), labels= function(x) highlight(x, "Average", "red"))

corr_matrix_sorted2

@@

```{r}

corr <- benchmark_corr(deconv_data = deconv_Thomas, true_estimates = truth_Thomas, dict = dict_GSE72056, key = "Samples")
p <- plot_corrplots(store_corrs = corr, key = "Samples", title = "Thomas")
p
# corrplots$Macrophages <- corrplots$Macrophages + rremove("y.text")
# corrplots$Neutrophils <- corrplots$Neutrophils + rremove("y.text")
# summary_corrplot  <- ggarrange(plotlist = corrplots, ncol = 3, common.legend = T, widths = c(0.35, 0.35, 0.25) , legend = "bottom")
# 
# ggsave("Fig2_summary_corrplot.pdf", dpi = "print", width = 250, height = 100, units = "mm", scale = 2.5)
```
